---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bayCi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of bayCi is to ...

## Installation

<!-- You can install the released version of bayCi from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("bayCi") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cdmuir/bayCi")
```
## Example

This is a basic example which shows you how to solve a common problem:

### Read LICOR data

- determine format
- check for errors
- remove extraneous lines
- find covariate columns
- if given file name, read single file
- if given multiple file names, read and row bind
- if given directory, read all file names and row bind
- set class. raw_licor_data

#### Single file

```{r read-licor}
library(bayCi)
## basic example code
```

#### Combine multiple files

### Prepare data


## Meta

Please note that the 'bayCi' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
