---
title: "Fit a single Rapid $A-C_i$ Response (RACiR) curve"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fit a single Rapid $A-C_i$ Response (RACiR) curve}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bayCi)
library(dplyr)
library(gunit)
library(units)
```

In this vignette we will analyze a single Rapid $A-C_i$ Response (RACiR) curve using the `braycir()` (pronounced like "bracer"). The example data associted with the **bayCI** package comes from [Stinziano *et al.* (2017)](https://doi.org/10.1111/pce.12911). It contains RACiR curves from *Poplar deltoides* and the object is called `stinziano_etal_2017`. It can accessed once **bayCI** is loaded into your environment.

### Step 1: Convert data to the `racir` class

The `braycir()` function is for fitting a single RACiR curve. The `data` argument in the `braycir()` function must inherit class `racir`. This ensures that all required variables:

* are present in the data
* have the correct column name
* have proper scientific units

The `racir()` function will make a new `racir` object from a `data.frame` and validate it.

```{r step1}

df <- stinziano_etal_2017 %>%

  # The dataset contains multiple RACiR curves, so we will filter out all but one
  filter(curve_type == "RACiR 0 to 500", plant_id == "A") %>%

  # Set units
  mutate(
    Ci    = set_units( Ci,    umol / mol     ),
    A     = set_units( A,     umol / m^2 / s ),
    Tleaf = set_units( Tleaf, degreeC        ),
    PARi  = set_units( PARi,  umol / m^2 / s ),
    E     = set_units( E,     mol / m^2 / s  ),
    gsc   = set_units( gsc,   mol / m^2 / s  ),
    Cs    = set_units( Cs,    umol / mol     ),
    Cr    = set_units( Cr,    umol / mol     ),
    Pa    = set_units( Pa,    kPa            )
  ) %>%
  
  # Following Sharkey et al. (2007), bayCi uses Pa units
  mutate(
    Pci = set_units(Ci * Pa, Pa),
    Pgsw = convert_conductance(gsc, P = Pa, Temp = Tleaf)$`umol/m^2/s/Pa`
  )

rcr <- racir(df)

class(rcr)

rcr %>%
  select(A, Ci) %>%
  mutate_if(is.numeric, signif, digits = 3) %>%
  head() %>%
  knitr::kable()

```

### Step 2: Convert empty chamber RACiR correction data to the `empty` class

Raw RACiR data be corrected using a "blank" curve measured on an empty chamber. These data are passed to `braycir()` using the `empty`, which must inherit class `empty`. This performs the same set of checks as the `racir` class. The `empty()` function will make a new `empty` object from a `data.frame` and validate it. The correction curve from Stinziano *et al.* (2017) comes with the **bayCi** package and can be accessed from `stinziano_etal_2017_empty`.

```{r step2}

df <- stinziano_etal_2017_empty %>%
  
  # Set units
  mutate(
    A     = set_units( A,     umol / m^2 / s ),
    Ci    = set_units( Ci,    umol / mol     ),
    Pa    = set_units( Pa,    kPa            ),
    Tleaf = set_units( Tleaf, degreeC        )
  ) %>%
  
  # Following Sharkey et al. (2007), bayCi uses Pa units
  mutate(
    Pci = set_units(Ci * Pa, Pa)
  )

mty <- empty(df)

class(mty)

mty %>%
  mutate_if(is.numeric, signif, digits = 3) %>%
  head() %>%
  knitr::kable()

```

### References

Sharkey TD, CJ Bernacchi, GD Farquhar, EL Singsaas. 2007. [Fitting photosynthetic carbon dioxide response curves for C$_3$ leaves](https://doi.org/10.1111/j.1365-3040.2007.01710.x). *Plant, Cell & Environment* 30(9): 1035--1040.

Stinziano JR, PB Morgan, DJ Lynch, AJ Saathoff, DK McDermitt, DT Hanson. 2017. [The rapid $A-C_i$ response: photosynthesis in the phenomic era](https://doi.org/10.1111/pce.12911). *Plant, Cell & Environment* 40(8): 1256--1262.