---
title: "Fit a single Rapid $A-C_i$ Response (RACiR) curve"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fit a single Rapid $A-C_i$ Response (RACiR) curve}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bayCi)
library(dplyr)
library(gunit)
library(units)
```

In this vignette we will analyze a single Rapid $A-C_i$ Response (RACiR) curve using the `braycir()` (pronounced like "bracer"). The example data associted with the **bayCI** package comes from [Stinziano *et al.* (2017)](https://doi.org/10.1111/pce.12911). It contains RACiR curves from *Poplar deltoides* and the object is called `stinziano_etal_2017`. It can accessed once **bayCI** is loaded into your environment.

### Step 1: Convert data to the `racir` class

The `braycir()` function is for fitting a single RACiR curve. The `data` argument in the `braycir()` function must inherit class `racir`. This ensures that all required variables:

* are present in the data
* have the correct column name
* have proper scientific units

The `racir()` function will make a new `racir` object from a `data.frame` and validate it.

```{r step1}

df <- stinziano_etal_2017 %>%
  
  # Set units
  mutate(
    A     = set_units( A,         umol / m^2 / s ),
    Tleaf = set_units( Tleaf,     degreeC        ),
    Q     = set_units( Q,         umol / m^2 / s ),
    E     = set_units( E,         mol / m^2 / s  ),
    gsc   = set_units( gsw / 1.6, mol / m^2 / s  ),
    gtc   = set_units( gtc,       mol / m^2 / s  ),
    CO2_r = set_units( CO2_r,     umol / mol     ),
    CO2_s = set_units( CO2_s,     umol / mol     ),
    Pa    = set_units( Pa,        kPa            ),
    Pci   = set_units( Pci,       Pa             )
  ) %>%
  
  # Following Sharkey et al. (2007), bayCi uses Pa units
  mutate(
    Pcr = set_units(CO2_r * Pa, Pa),
    Pcs = set_units(CO2_s * Pa, Pa),
    Pgsc = convert_conductance(gsc, P = Pa, Temp = Tleaf)$`umol/m^2/s/Pa`
  ) %>%
  
  select(A, Cr = CO2_r, Cs = CO2_s, E, gsc, gtc, Pa, Pcr) %>%
  
  filter(Cr > set_units(10, umol / mol), Cr < set_units(480, umol / mol))

rcr <- racir(df)

class(rcr)

rcr %>%
  select(A, Pcr) %>%
  mutate_if(is.numeric, signif, digits = 3) %>%
  head() %>%
  knitr::kable()

```

### Step 2: Convert empty chamber RACiR correction data to the `empty` class

Raw RACiR data be corrected using a "blank" curve measured on an empty chamber. These data are passed to `braycir()` using the `empty`, which must inherit class `empty`. This performs the same set of checks as the `racir` class. The `empty()` function will make a new `empty` object from a `data.frame` and validate it. The correction curve from Stinziano *et al.* (2017) comes with the **bayCi** package and can be accessed from `stinziano_etal_2017_empty`.

```{r step2}

df <- stinziano_etal_2017_empty %>%
  
  # Set units
  mutate(
    A  = set_units( A,  umol / m^2 / s ),
    Cr = set_units( Cr, umol / mol     )
  )

mty <- empty(df)

class(mty)

mty %>%
  mutate_if(is.numeric, signif, digits = 3) %>%
  head() %>%
  knitr::kable()

```

### References

Sharkey TD, CJ Bernacchi, GD Farquhar, EL Singsaas. 2007. [Fitting photosynthetic carbon dioxide response curves for C$_3$ leaves](https://doi.org/10.1111/j.1365-3040.2007.01710.x). *Plant, Cell & Environment* 30(9): 1035--1040.

Stinziano JR, PB Morgan, DJ Lynch, AJ Saathoff, DK McDermitt, DT Hanson. 2017. [The rapid $A-C_i$ response: photosynthesis in the phenomic era](https://doi.org/10.1111/pce.12911). *Plant, Cell & Environment* 40(8): 1256--1262.